---
title: "607 Assignment3- String  "
author: "Hui (Gracie) Han
date: "Sep16, 2018"
output:  html_document:  ---
Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to problems 3 and 4 from chapter 8 of Automated Data Collection in R.  Problem 9 is extra credit.  You may work in a small group, but please submit separately with names of all group participants in your submission.
Problem 3. Copy the introductory example. The vector name stores the extracted names.
[1] "Moe Szyslak" "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
[4] "Ned Flanders" "Simpson, Homer" "Dr. Julius Hibbert"
(a) Use the tools of this chapter to rearrange the vector so that all elements conform to
the standard first_name last_name.--will work on 3a after completed 3b and 3C
(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and
Dr.).----- will work on b first, then do a, which makes more logical sense
(c) Construct a logical vector indicating whether a character has a second name.


first, set the library and load the original data
```{r}
library(tidyverse)
library (stringr)
library(stringi)
getwd()
```

```{r}
NamesInput <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
NamesInput
```
Do question 3B first 
3b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.)
# Get all the names as they are first
```{r}
Names1<-unlist(str_extract_all(NamesInput, "[[:alpha:]., ]{2,}"))
Names1
```

```{r}
NamesWtitlesLogic = str_detect(Names1, "Rev.|Dr.")
NamesWtitlesLogic
```
3c) Construct a logical vector indicating whether a character has a second name.
to solve this: detect a name that has space in between, then that is the second name
```{r}
Names1
NamesSecond <- str_detect (Names1, "[A-Z]{1}\\.")
NamesSecond
```
3C) Construct a logical vector indicating whether a character has a second name. To solve this, we do a word count of the strings.  All regular namesshould have 2 strings.  The 2nd named string have three strings, that's the answer.  
```{r}
## remove the titles first
NameWOtitle <- str_replace (Names1,"Rev.|Dr.", replacement = "" )
NameWOtitle
# count the strings
NamesCount <-str_count(NameWOtitle, "\\w+")
NamesCount
```
As seen from last run, only the 2nd element have 3 strings (2nd name), construct a logical vector for that
```{r}
NamesCountGT2 <- str_detect (NamesCount, "3")
NamesCountGT2
```
NExt, do 3a, (a) Use the tools of this chapter to rearrange the vector so that all elements conform to
the standard first_name last_name.
## remove the titles, replace the title with space
```{r}
# str_replace(string, pattern, replacement)
NameWOtitle <- str_replace (Names1,"Rev.|Dr.", replacement = "" )
NameWOtitle
```

Next, for Burns, C. MOngomery, the middle nmae need to be removed
for two people (LastName, FirstName), their name order need to be re-arranged
remove middle names -

```{r}
namesWOMidName <- str_replace(NameWOtitle, "\\s[A-z]\\. ", " ")
### pattern: \-- match a space character, [A-z]--followed by a chacter, -- \ followed by a coma (,)
#  replace them with a nothing
namesWOMidName
```
Split those names("Burns, MOntgemety" & "Simpson,HOmer") separated by a comma into two vectors, trim, and reverse order.
```{r}
 splitnameTemp1 <- sapply(str_split(namesWOMidName, ","), str_trim)
 splitnameTemp1

 splitnameTemp2 <- sapply(splitnameTemp1,rev)
 splitnameTemp2

```
 Then paste the vectors together with a space in between. Then turn the list back into a vector
```{r}
for (i in 1:length(namesWOMidName)) {
  splitnameTemp2[i]<- paste(unlist(splitnameTemp2[i]), collapse = " ")  
  }
 
splitname7 <- unlist(splitnameTemp2)
splitname7
```

4. Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.
(a) [0-9]+\\$
this string extracts any number 0-9 at the end of string ($)

```{r}
String4a <- c("$243464","9090$09090")
string4aE <- str_extract(String4a,"[0-9]+\\$")
string4aE
```

(b) \\b[a-z]{1,4}\\b
this describes any lower case letter [a-z] between 1 to 4 charcters long {1,4}, with blanks (\\b) before and after 
```{r}
String4b <- c("ty"," z8B98$"," c "," 8SDF ","asdfg "," ssas ")
String4bE <- str_extract(String4b,"\\b[a-z]{1,4}\\b")
String4bE
```
(c) .*?\\.txt$
this evaluates strings with .txt at end ($)
```{r}
String4c <- c("Mydoc.doc", "Mydoc.txt", ".txt", ".xls")
String4cE <- str_extract (String4c, ".*?\\.txt$")
String4cE
```

(d) \\d{2}/\\d{2}/\\d{4}
this evaluates the patten with two forward slash (such as date DD/MM/YYYY format) with exactly 2 , 2, 4 characters long
```{r}
String4d <-  c("11/10/2008","12/2/2008 ","12/12\1999"," asdf ","2/12/2010 ", "01/01/99" )
String4dE <- str_extract (String4d, '\\d{2}/\\d{2}/\\d{4}')
String4dE
```

(e) <(.+?)>.+?</\\1>
this evaluates any <> with a forward slash within
```{r}
String4e <- c("<tag> myname/>","<tag>something</tag>")
String4eE <- str_extract(String4e,"<(.+?)>.+?</\\1>")
String4eE

```
